---
title: "Codebook example with SPSS dataset"
author: "Ruben Arslan"
date: "`r Sys.Date()`"
output:
  html_vignette:
    fig_width: 7
    fig_height: 6
vignette: >
  %\VignetteIndexEntry{SPSS dataset with metadata}
  \%VignetteKeyword{manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message = FALSE}
knit_by_pkgdown <- !is.null(knitr::opts_chunk$get("fig.retina"))
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(warning = TRUE, message = TRUE, error = FALSE, echo = TRUE)
library(dplyr)
library(codebook)
```

In this vignette, you can see how to use the metadata that is often already stored
in SPSS and Stata files. It's easy. All we need is the `rio::import` function.
For files with the right file extension, we can automatically pick the right way 
to import the data. Here, we're downloading straight from the Open Science Framework, 
so we have to specify the file extension.

We select a subset of variables, just to keep it short. The data were shared by
Emanuel Jauk in a project called [How alluring are dark personalities? The Dark Triad and attractiveness in speed dating](https://osf.io/j4fcb/).

Often, files imported from SPSS or Stata to R will not have their missings coded
properly. Here, that is not the case, but if you find yourself with such a dataset,
the `detect_missing` function makes it easy to recognise common ways to specify
missing data (e.g. negative values, labelled values, 99/999).

```{r}
darktriad <- rio::import("https://osf.io/j4fcb/download", format = "sav")
if (!knit_by_pkgdown) {
  darktriad <- darktriad %>%
  select(DG, sex, relStat, education, NPI_avg)
}
```


```{r}
metadata(darktriad)$name <- "How alluring are dark personalities? The Dark Triad and attractiveness in speed dating"
metadata(darktriad)$description <- paste0("The data to this speed dating study comes in two different formats: Personwise (one record for each individual) and dyadic (pairwise; one record for each date). The respective SPSS files are named \"DarkTriadDate_person.sav\" and \"DarkTriadDate_dyad.sav\".

### Download link
[Open Science Framework](https://osf.io/j4fcb/download)

### Personwise datafile 
The personwise datafile contains individual differences variables and perceiver and target effects according to the social relations model. These are centered marginal means that were calculated according to the formulae provided by Kenny, Kashy, and Cook (2006). These effects are not (!) based on multilevel analyses.

### Preprocessing
All rating variables (i.e., actual choice, friendship, short-term relationship etc.) were corrected for prior acquaintance, which means that dates wih prior acquaintance were excluded (set to missing) on a dyadic basis.

Variables are labeled in SPSS. 

### A list of important abbreviations, prefixes and suffixes:

* _acq = acquaintance (i.e., variables with this suffix are controlled for prior * acquaintance)
* avg = average
* _rat = rating variable
* _z = z-standardized score
* BC = booty call
* DG = dating group (three groups in this study)
* FIPI = five item personality inventory
* FS = friendship
* FWB = friends-with-benefits
* Int = Intelligence
* Like = Likeability
* LTR = long-term relationship
* MACHIV = mach-iv machiavellianism questionnaire
* N, E, O, A, C = Big5
* NPI = narcissistic personality inventory
* ONS = one night stand
* P = perceiver
* PA = physical attractiveness
* PercEff = perceiver effect
* SD = speed dating
* SRM = social relations model
* SRP = self-report psychopathy scale
* STR = short-term relationship
* T = target
* TargEff = target effect


")
metadata(darktriad)$identifier <- "https://osf.io/jvk3u/"
metadata(darktriad)$datePublished <- "2015-10-07"
metadata(darktriad)$creator <- list(
      "@type" = "Person",
      givenName = "Emanuel", familyName = "Jauk",
      email = "emanuel.jauk@uni‐graz.at", 
      affiliation = list("@type" = "Organization",
        name = "Karl‐Franzens‐Universität Graz, Austria"))
metadata(darktriad)$citation <- "Jauk, E., Neubauer, A. C., Mairunteregger, T., Pemp, S., Sieber, K. P., & Rauthmann, J. F. (2016). How alluring are dark personalities? The Dark Triad and attractiveness in speed dating. European Journal of Personality, 30(2), 125-138."
metadata(darktriad)$url <- "https://osf.io/j4fcb/"
metadata(darktriad)$temporalCoverage <- "2015" 
metadata(darktriad)$spatialCoverage <- "Graz, Austria" 
metadata(darktriad)$distribution = list(
  list("@type" = "DataDownload",
       "requiresSubscription" = "http://schema.org/True",
       "encodingFormat" = "https://www.loc.gov/preservation/digital/formats/fdd/fdd000469.shtml",
       contentUrl = "https://osf.io/j4fcb/download")
)
```

```{r}
# We don't want to look at the code in the codebook.
knitr::opts_chunk$set(warning = TRUE, message = TRUE, echo = FALSE)
```

Now, we can immediately generate a codebook.

```{r cb}
codebook(darktriad, survey_repetition = "single",
         metadata_table = knit_by_pkgdown, metadata_json = knit_by_pkgdown)
```

`r ifelse(knit_by_pkgdown, '', '### Codebook table')`

```{r}
if (!knit_by_pkgdown) {
  codebook:::escaped_table(codebook_table(darktriad))
}
```

