---
title: "Codebook example with SPSS dataset"
author: "Ruben Arslan"
date: "`r Sys.Date()`"
output:
  html_vignette:
    fig_width: 7
    fig_height: 6
vignette: >
  %\VignetteIndexEntry{Example with SPSS dataset}
  \%VignetteKeyword{manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message = FALSE}
knit_by_pkgdown <- !is.null(knitr::opts_chunk$get("fig.retina"))
pander::panderOptions("table.split.table", Inf)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(warning = TRUE, message = TRUE, error = TRUE, echo = TRUE)
library(dplyr)
library(codebook)
```

In this vignette, you can see how to use the metadata that is often already stored
in SPSS and Stata files. It's easy. All we need is the `rio::import` function.
For files with the right file extension, we can automatically pick the right way 
to import the data. Here, we're downloading straight from the Open Science Framework, 
so we have to specify the file extension.

We select a subset of variables, just to keep it short. The data were shared by
Emanuel Jauk in a project called [How alluring are dark personalities? The Dark Triad and attractiveness in speed dating](https://osf.io/j4fcb/).

Often, files imported from SPSS or Stata to R will not have their missings coded
properly. Here, that is not the case, but if you find yourself with such a dataset,
the `detect_missings` function makes it easy to recognise common ways to specify
missing data (e.g. negative values, labelled values, 99/999).

```{r}
darktriad <- rio::import("https://osf.io/j4fcb/download", format = "sav") %>%
  select(DG, sex, relStat, education, NPI_avg)
if (!knit_by_pkgdown) knitr::opts_chunk$set(echo = FALSE)
```

Now, we can immediately generate a codebook.

```{r cb}
codebook(darktriad, survey_repetition = "single",
         metadata_table = knit_by_pkgdown, metadata_json = knit_by_pkgdown)
```


`r ifelse(knit_by_pkgdown, '', '### Codebook table')`

```{r}
if (!knit_by_pkgdown) {
  codebook:::escaped_table(codebook_table(darktriad))
}
```

