---
title: "Codebook example with formr.org data"
author: "Ruben Arslan"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
    fig_width: 7
    fig_height: 7
    fig_retina: null
vignette: >
  %\VignetteIndexEntry{Using formr.org data and metadata}
  \%VignetteKeyword{codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


In this vignette, you can see what a codebook generated from a dataset with rich
metadata looks like. This dataset includes mock data for a short German Big Five 
personality inventory and an age variable. The dataset follows the format created
when importing data from [formr.org](https://formr.org). However, data imported
using the `haven` package uses similar metadata. You can also add such metadata
yourself, or use the codebook package for unannotated datasets.

As you can see below, the `codebook` package automatically computes reliabilities
for multi-item inventories, generates nicely labelled plots and outputs summary statistics.
The same information is also stored in a table, which you can export to various formats.
Additionally, `codebook` can show you different kinds of (labelled) missing values, and show you common 
missingness patterns.
As _you_ cannot see, but _[search engines](https://toolbox.google.com/datasetsearch)_
will, the `codebook` package also generates [JSON-LD](https://json-ld.org/) metadata for the [dataset](https://developers.google.com/search/docs/data-types/dataset). If you share your codebook as an HTML file online, this metadata should make it easier for others
to find your data. [See what Google sees here](https://search.google.com/structured-data/testing-tool#url=https%3A%2F%2Frubenarslan.github.io%2Fcodebook%2Farticles%2Fcodebook.html).

```{r warning=FALSE,message=FALSE}
knit_by_pkgdown <- !is.null(knitr::opts_chunk$get("fig.retina"))
knitr::opts_chunk$set(warning = FALSE, message = TRUE, error = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())

library(codebook)
data("bfi", package = 'codebook')
if (!knit_by_pkgdown) {
  library(dplyr)
    bfi <- bfi %>% select(-starts_with("BFIK_extra"),
                        -starts_with("BFIK_open"),
                        -starts_with("BFIK_consc"))
}
set.seed(1)
bfi$age <- rpois(nrow(bfi), 30)
library(labelled)
var_label(bfi$age) <- "Alter"
```

By default, we only set the required metadata attributes `name` and `description`
to sensible values. However, there is a number of attributes you can set to 
describe the data better. [Find out more](https://developers.google.com/search/docs/data-types/dataset).

```{r}
metadata(bfi)$name <- "MOCK Big Five Inventory dataset (German metadata demo)"
metadata(bfi)$description <- "a small mock Big Five Inventory dataset"
metadata(bfi)$identifier <- "doi:10.5281/zenodo.1326520"
metadata(bfi)$datePublished <- "2016-06-01"
metadata(bfi)$creator <- list(
      "@type" = "Person",
      givenName = "Ruben", familyName = "Arslan",
      email = "ruben.arslan@gmail.com", 
      affiliation = list("@type" = "Organization",
        name = "MPI Human Development, Berlin"))
metadata(bfi)$citation <- "Arslan (2016). Mock BFI data."
metadata(bfi)$url <- "https://rubenarslan.github.io/codebook/articles/codebook.html"
metadata(bfi)$temporalCoverage <- "2016" 
metadata(bfi)$spatialCoverage <- "Goettingen, Germany" 
```

```{r}
# We don't want to look at the code in the codebook.
knitr::opts_chunk$set(warning = TRUE, message = TRUE, echo = FALSE)
```

```{r cb}
codebook(bfi, metadata_table = knit_by_pkgdown, metadata_json = TRUE)
```


`r ifelse(knit_by_pkgdown, '', '### Codebook table')`

```{r}
if (!knit_by_pkgdown) {
  codebook:::escaped_table(codebook_table(bfi))
}
```
