```{r setup,eval=TRUE,echo=FALSE}
if (!exists("indent")) {
	indent = '#' # ugly hack so _regression_summary can be "spun" (variables included via `r ` have to be available)
}
if (exists("testing")) {
	results = data.frame()
	repeated_survey = 'single'
	reliabilities = list()
	missingness_report = TRUE
}
```

`r indent`# Survey overview

```{r}
codebook_survey_overview(results, repeated_survey)
```



`r indent`# Scales

```{r scales,results='asis'}
vars = names(results)
for (i in seq_along(vars)) {
	var = vars[i]
	scale = results[[ var ]]
	scale_info = attributes(scale)
	if ( !is.null(scale_info) && exists("scale", scale_info)) {
	    cat(codebook_component_scale( scale, dplyr::select(results, .data$session, dplyr::starts_with(scale_info$scale)), reliabilities[[var]], indent))
	  }
}
```

`r indent`# Single items

```{r items,results='asis'}
for (i in seq_along(vars)) {
	var = vars[i]
	item = results[[ var ]]
	item_info = attributes(item)
	if ( !is.null(item_info)) {
		if (exists("part_of_scale", item_info) || exists("scale", item_info) || var %in% c("created", "modified", "expired", "ended")) {
			next
		} else if (exists("item", item_info)) {
			cat(codebook_component_single_item( item, results, indent ))
		} else {
			cat(codebook_component_fallback( item, results, var, indent))
		}
	}
}
```


`r indent`# Missingness report {.tabset .tabset-sticky}

There were `r ended(results)` rows completed, `r started` who entered any information, `r only_viewed` only viewed the first page. There are `r expired(results)` expired rows (people who did not finish filling out in the requested time frame). 

### Missingness finishers

among those who finished the survey

```{r missingness_all_setup}
missingness = missingness_patterns(
	dplyr::select(dplyr::filter(results, !is.na(ended)), -expired, -ended) )
```
```{r missingness_all}
pander::pander(missingness)
```



### Missingness starters

among those who started the survey

```{r missingness_starters_setup,results='markup'}
if (missingness_report) {
  missingness = missingness_patterns(
  	dplyr::filter(results, !is.na(modified)) )
} else {
  cat("No missingness report requested.")
}
```
```{r missingness_starters}
if (missingness_report) {
  pander::pander(missingness)
} else {
  cat("No missingness report requested.")
}
```


### Item table
```{r}

item_index = dplyr::select(as.data.frame(items(results)), -choice_list, -index)
item_index = dplyr::mutate(item_index, name = paste0('<a href="#', name, '">', name, '</a>'))
DT::datatable(item_index, rownames = FALSE, filter = "top", extensions = 'Buttons', 
escape = setdiff(names(item_index), 'name'),
options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
    pageLength = 200
  ))
```
