```{r setup,eval=TRUE,echo=FALSE}
if (!exists("indent")) {
	indent <- '#' # ugly hack so _regression_summary can be "spun" (variables included via `r ` have to be available)
}
if (exists("testing")) {
	item <- 1:10
	item_name <- safe_name <- "yay"
	attributes(item) <- list(label = 'yayya')
}

item_attributes <- recursive_escape(attributes(item))
html_item_name <- recursive_escape(item_name)
item_label <- ifelse(is.null(item_attributes) || is.null(item_attributes$label), 
                     "", item_attributes$label)
item_info <- item_attributes$item
choices <- item_attributes$labels
```

`r indent`## `r html_item_name` {#`r safe_name` .tabset}

`r item_label`

`r indent`### Distribution {#`r safe_name`_distribution}
```{r setup_missings}
show_missings <- FALSE
if (haven::is.labelled(item)) {
  missings <- item[is.na(haven::zap_missing(item))]
  attributes(missings) <- attributes(item)
  if (!is.null(attributes(item)$labels)) {
    attributes(missings)$labels <- attributes(missings)$labels[is.na(attributes(missings)$labels)]
    attributes(item)$labels <- attributes(item)$labels[!is.na(attributes(item)$labels)]
  }
  if (is.numeric(item)) {
    show_missings <- length(unique(haven::na_tag(missings))) > 1
    item <- haven::zap_missing(item)
  }
  if (length(item_attributes$labels) == 0 && is.numeric(item)) {
    item <- haven::zap_labels(item)
  }
}
item_nomiss <- item[!is.na(item)]

# unnest mc_multiple and so on
if (
  is.character(item_nomiss) &&
  stringr::str_detect(item_nomiss, stringr::fixed(", ")) &&
  (exists("type", item_info) && 
    stringr::str_detect(item_info$type, pattern = stringr::fixed("multiple")))
  ) {
  item_nomiss <- unlist(stringr::str_split(item_nomiss, pattern = stringr::fixed(", ")))
}
attributes(item_nomiss) <- attributes(item)

old_height <- knitr::opts_chunk$get("fig.height")
non_missing_choices <- item_attributes[["labels"]]
many_labels <- length(non_missing_choices) > 7
go_vertical <- !is.numeric(item_nomiss) || many_labels
if ( go_vertical ) {
  # numeric items are plotted horizontally (because that's what usually expected)
  # categorical items are plotted vertically because we can use the screen real estate better this way

	if (is.null(choices) || 
	    dplyr::n_distinct(item_nomiss) > length(non_missing_choices)) {
		non_missing_choices <- unique(item_nomiss)
		names(non_missing_choices) <- non_missing_choices
	}
  choice_multiplier <- old_height/6.5
	new_height <- 2 + choice_multiplier * length(non_missing_choices)
	new_height <- ifelse(new_height > 20, 20, new_height)
	new_height <- ifelse(new_height < 1, 1, new_height)
	knitr::opts_chunk$set(fig.height = new_height)
}

wrap_at <- knitr::opts_chunk$get("fig.width") * 10
```
```{r distribution}
# todo: if there are free-text choices mingled in with the pre-defined ones, don't show
# todo: show rare items if they are pre-defined
# todo: bin rare responses into "other category"
if (!length(item_nomiss)) {
  cat("No non-missing values to show.")
} else if (is.numeric(item_nomiss) || dplyr::n_distinct(item_nomiss) < 20) {
  plot_labelled(item_nomiss, item_name, wrap_at, go_vertical)
} else {
	cat(dplyr::n_distinct(item_nomiss), " unique, categorical values, so not shown.")
}
knitr::opts_chunk$set(fig.height = old_height)
```

`r sum(is.na(item))` missings.

`r indent`### Summary statistics {#`r safe_name`_summary}
```{r summary}
attributes(item) <- item_attributes
df = data.frame(item)
names(df) = html_item_name
knitr::kable(codebook_table(df), escape = TRUE)
```

`r ifelse(show_missings, paste0(indent, '### Missing value types {#', safe_name, '_missings}'), '')`
```{r missings}
if (show_missings) {
  plot_labelled(missings, item_name, wrap_at)
}
```

`r ifelse(!is.null(item_info), paste0(indent, '### Item {#', safe_name, '_item}'), '')`

```{r item_info}
if (!is.null(item_info)) {
  # don't show choices again, if they're basically same thing as value labels
  if (!is.null(choices) && !is.null(item_info$choices) && 
    all(names(na.omit(choices)) == item_info$choices) &&
    all(na.omit(choices) == names(item_info$choices))) {
    item_info$choices <- NULL
  }
  item_info$label_parsed <- 
    item_info$choice_list <- item_info$study_id <- item_info$id <- NULL
  pander::pander(item_info)
}
```


`r ifelse(!is.null(choices) && length(choices) && length(choices) < 30, paste0(indent, '### Value labels {#', safe_name, '_labels}'), '')`
```{r choices}
if (!is.null(choices) && length(choices) && length(choices) < 30) {
	pander::pander(as.list(choices))
}
```

